R Notebook

### 2021-12-01 src/main/r/numeric_vs_hpo_for_acute_kidney_failure.Rmd
minor tweak

---
title: "R Notebook"
output: html_notebook
---

@@

df_labs_and_outcomes <- df_labs %>% filter(loinc %in% c('2160-0', '3094-0', '6299-2', '2823-3')) %>%
  as_tibble() %>%
  select(-min_diag_date, -rel_date) %>% ## these two columns can be removed from the sql query
  ##filter(medical_record_number %in% c('2715515', '3087585')) %>% ## test with a few patient
  left_join(df_cohort, by = 'medical_record_number') %>%
  mutate(lab_date = ymd(lab_date), min_diag_date = ymd(min_diag_date)) %>%
  mutate(lab_date_rel_to_diag = as.duration(interval(min_diag_date, lab_date)) / ddays()) %>%
  mutate(window_num = cut(lab_date_rel_to_diag, c(-Inf, -180, 0, Inf))) %>%
##select(medical_record_number, loinc, lab_date, min_diag_date, lab_date_rel_to_diag, window_num)
  filter(window_num %in% c('(-Inf,-180]', '(-180,0]')) %>%
  arrange(medical_record_number, loinc, -lab_date_rel_to_diag) %>%
  group_by(medical_record_number, loinc, window_num) %>%
  mutate(sequence = row_number()) %>%
  #select(medical_record_number, loinc, lab_date, min_diag_date, lab_date_rel_to_diag, window_num, sequence) %>%
  ungroup() %>%
  filter(sequence == 1) %>%
  mutate(outcome = if_else(window_num == '(-180,0]', 'abnormal', 'normal'))

@@

```{r}
require(furrr)
plan(multisession, workers = 4)

@@

```{r}
df_one_loinc <- df_labs_and_outcomes %>% filter(loinc == '1742-6')

@@

lr_H <- lr_for_hpo_H(df_train = df_train, df_test = df_test)
roc_comparison <- compare_rocs(lr_H[[5]], lr_H[[6]])
roc_comparison <- bind_cols(roc_comparison, valid_lab_outcomes %>% filter(interpretation == 'H'))
roc_comparisons$H <- roc_comparison

>>>>

---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

@@

df_labs_and_outcomes <- df_labs %>% filter(loinc %in% c('2160-0', '3094-0', '6299-2', '2823-3')) %>%
  as_tibble() %>%
  select(-min_diag_date, -rel_date) %>% ## these two columns can be removed from the sql query
  ##filter(medical_record_number %in% c('2715515', '3087585')) %>% ## test with a few patient
  left_join(df_cohort, by = 'medical_record_number') %>%
  mutate(lab_date = ymd(lab_date), min_diag_date = ymd(min_diag_date)) %>%
  mutate(lab_date_rel_to_diag = as.duration(interval(min_diag_date, lab_date)) / ddays()) %>%
  mutate(window_num = cut(lab_date_rel_to_diag, c(-Inf, -100, 0, Inf))) %>%
##select(medical_record_number, loinc, lab_date, min_diag_date, lab_date_rel_to_diag, window_num)
  filter(window_num %in% c('(-Inf,-100]', '(-100,0]')) %>%
  arrange(medical_record_number, loinc, -lab_date_rel_to_diag) %>%
  group_by(medical_record_number, loinc, window_num) %>%
  mutate(sequence = row_number()) %>%
  #select(medical_record_number, loinc, lab_date, min_diag_date, lab_date_rel_to_diag, window_num, sequence) %>%
  ungroup() %>%
  filter(sequence == 1) %>%
  mutate(outcome = if_else(window_num == '(-100,0]', 'abnormal', 'normal'))

@@

```{r max.output=-1}
require(furrr)
plan(multisession, workers = 4)

@@

```{r}
df_one_loinc <- df_labs_and_outcomes %>% filter(loinc == '2160-0')

@@

lr_H <- lr_for_hpo_H(df_train = df_train, df_test = df_test)
roc_comparison <- compare_rocs(lr_H[[5]], lr_H[[6]])
roc_comparison <- bind_cols(roc_comparison)
roc_comparison$H <- roc_comparison
